### 2023-03-27 seitan/seitan.tex
ch2

Within you, in upper Queen Anne, lives this story's protagonist.
They recently moved into you, far too recently to have deep enough social roots for the epidemiological circumstances of the year in question.
Queen Anne is a beautiful neighborhood,
full of cherry blossom trees stunning in the spring,
radio towers that one can stand at the base of and crane their neck to see the top in a dizzying twist of perspective
(except during wildfire season, when, incidentally, one's newly-acquired KN95s find a secondary use),
and artfully manicured flower gardens afore multimillion-dollar homes,
which make our protagonist feel keenly alienated in their 800sqft apartment.
The protagonist copes with quarantine, in part, by attending ThursDz, now occurring virtually,
and they begin to long for a particular food of home.
%
Said home, Pittsburgh Appalachia USA, is famous for many foods,
but they long in particular for a less famous one: the humble seitan wing.

@@

It's fall 2020, and you are Google's search results for ``seitan wings recipe''.

@@

\chapter{4}{Texture}

@@

\noindent \begin{tabular}{p{0.95\textwidth}}
	{\bf Ingredients (Wing; dry)} \\
	\hline
	{\em 14 oz} -- Vital wheat gluten \\
	{\em 1 oz} -- Nutritional yeast (or parmesan) \\
	{\em 2 tsp} -- Salt \\
	{\em 3 Tbsp} -- Spices: rosemary, thyme, onion or garlic powder, and white pepper \\
	\\
	{\bf Ingredients (Wing; wet)} \\
	\hline
	{\em 12 oz} -- Water (or chicken stock, for irony) \\
	{\em 6 oz} -- Tomato paste \\
	{\em 2 oz} -- Olive oil \\
	\\
	{\bf Ingredients (Buffalo)} \\
	\hline
	{\em 2 Tbsp} -- Butter (omit for vegans) \\
	{\em 2 Tbsp} -- Hot sauce (Frank's is canonical, but they prefer Cholula) \\
	\\
	{\bf Ingredients (Bluech)} \\
	\hline
	{\em 1/4 cup} -- Blue cheese (a nice, creamy pungent one from Penn Mac) \\
	{\em 1/4 cup} -- Buttermilk (you can substitute but it really makes a difference) \\
	{\em Spoonful} -- Plain greek yogurt or sour cream, for consistency, optional \\
	\\
	{\bf Method} \\
	\hline
\setlength{\parskip}{0.5em}
	In two bowls, separately mix the dry and wet wingredients. Combine and knead for about 5 minutes, until coherent but also tears easily. Add more liquid or gluten as necessary, a little at a time.

>>>>

Within you, in upper Queen Anne, lives this story's protagonist.
They recently moved into you, far too recently to have deep enough social roots for the epidemiological circumstances of the year in question.
Queen Anne is a beautiful neighborhood,
full of cherry blossom trees stunning in the spring,
radio towers that one can stand at the base of and crane their neck to see the top in a dizzying twist of perspective
(except during wildfire season, when, incidentally, one's newly-acquired KN95s find a secondary use),
and artfully manicured flower gardens afore multimillion-dollar homes,
which make our protagonist feel keenly alienated in their 800sqft apartment.
They cope with quarantine, in part, by attending the now-virtual ThursDz,
%, now occurring virtually,
and they begin to long for a particular food of home.
%
Said home, Pittsburgh Appalachia USA, is famous for many foods,
but they long in particular for a less famous one: the humble seitan wing.

@@

It's fall 2020, and you are Google's search results for ``seitan wings recipe''.
You know what a seitan wing is.

You profess to contain one and a half million results.
The protagonist doesn't have quite that much time on their hands,
but they do have a lot, so they try (or at least read) everything on your first page.
You don't seem to agree with yourself very much, they notice:
you sometimes suggest breading the wing (which the protagonist knows to be wrong),
you sometimes suggest BBQ or garlic sauce instead of buffalo (which is noncanonical, but fine),
but most bafflingly, you suggest as many different ways of cooking the seitan as there are recipes.
Most often, you suggest to boil it,
which the protagonist gamely tries,
all the while remembering a story they heard long ago about how their mom's dad was so bad a cook she once caught him boiling a steak.
It sucks.
You say they should boil it then bake it;
you say they should boil it then saut\'e it;
you say they should saut\'e it then boil it;
you say they should fry it;
you say they should not just fry it, because it will leave the inside raw and gummy (this, for once, is true),
you say they should bake it;
you say they should bake it in broth;
you say they should bake it dry tossed in oil.

Among these, the last idea at least produces something both edible and texturally close to the crispy exterior the protagonist remembers, but it is only ``close'' like standing on the next tallest mountain peak and looking across the way at the one you {\em meant} to climb is ``close''.
Everything you say is touched by the spectre of health food writing,
because your reader must be into \textasciitilde{}vegan alternatives\textasciitilde{}.
Drowning in your million useless results the protagonist knows one truth deep in their heart: Seitan wings is not a health food.

Months pass, and the protagonist does not talk to you anymore.
They play Breath of the Wild in Japanese (which had long been a goal of theirs),
they play lots of gay VNs on itch dot io,
they practice Touhou music on the piano,
%they play Touhou,
and they play Netrunner worlds online over an enchanting coq au vin their elderly neighbor Ellen prepared for their nascent no-contact food relationship.

It's December 25, and thinking of you again, they pose your unanswered mystery to Tw*tter.
A Seattle friend replies, at long last, with the secret:

Steam, then fry.

@@

\chapter{4}{Tenderness}

@@

\noindent \begin{tabular}{p{0.95\textwidth}}
	{\bf Ingredients (Wing; dry)} \\
	\hline
	{\em 14 oz} -- Vital wheat gluten \\
	{\em 1 oz} -- Nutritional yeast (or parmesan) \\
	{\em 3 Tbsp} -- Spices: rosemary, thyme, onion or garlic powder, and white pepper \\
	{\em 2 tsp} -- Salt \\
	\\
	{\bf Ingredients (Wing; wet)} \\
	\hline
	{\em 12 oz} -- Water (or chicken stock, for irony) \\
	{\em 6 oz} -- Tomato paste \\
	{\em 2 oz} -- Olive oil \\
	\\
	{\bf Ingredients (Buffalo)} \\
	\hline
	{\em 2 Tbsp} -- Butter (omit for vegans) \\
	{\em 2 Tbsp} -- Hot sauce (Frank's is canonical, but they prefer Cholula) \\
	\\
	{\bf Ingredients (Bluech)} \\
	\hline
	{\em 1/3 cup} -- Blue cheese (a nice, creamy pungent one from Penn Mac) \\
	{\em 1/3 cup} -- Buttermilk (you can substitute but it really makes a difference) \\
	{\em Spoonful} -- Plain greek yogurt or sour cream, for consistency, optional \\
	\\
	{\bf Method} \\
	\hline
\setlength{\parskip}{0.5em}
	In two bowls, separately mix the dry and wet wingredients. Combine and knead for about 5 minutes, until coherent but also tears easily. Add more liquid or gluten as necessary, a little at a time.
